United Monoids

### 2022-01-12 paper/main.tex
Tweak references
Fix backticks (bad font)

hasEdge :: Ord a => a -> a -> TGraph a -> Bool
hasEdge x y graph = case induce (\a -> a == x || a == y) graph of
    Nothing -> False
    Just sub -> (x,y) `elem` edgeSet sub -- Here !\h{sub}! can only contain vertices !\h{x}! and !\h{y}!
!\rule[2mm]{\textwidth}{0.4pt}!
\end{lstlisting}

@@

Section~\S\ref{sec-labelled} will introduce a few missing tools for working with
generalised edge-labelled graphs. With these tools, and the Floyd-Warshall-Kleene
algorithm~\cite{hopcroft_ullman}\cite{kleene1951representation}, we will be able
to interpret trees over an arbitrary semiring and satisfy the sequential
composition requirements. An implementation can be found
in~\cite{alga_haskell}.

@@

\noindent
It is useful to combine edge-labelled graphs with the sequential composition
law described in the previous section~(\S\ref{sec-preorder}). By computing the
reflexive and transitive closure of an edge-labelled graph, it is possible to
solve a variety of semiring optimisation problems, e.g.,
see~\cite{2013_semirings_dolan}\cite{mohri2002semiring}.

>>>>

hasEdge :: Ord a => a -> a -> TGraph a -> Bool
hasEdge x y graph = case induce (\a -> a == x || a == y) graph of
    Nothing -> False
    Just sub -> elem (x,!\,!y) (edgeSet sub) -- Here !\h{sub}! can only contain vertices !\h{x}! and !\h{y}!
!\rule[2mm]{\textwidth}{0.4pt}!
\end{lstlisting}

@@

Section~\S\ref{sec-labelled} will introduce a few missing tools for working with
generalised edge-labelled graphs. With these tools, and the Floyd-Warshall-Kleene
algorithm~\cite{hopcroft_ullman}\cite{kleene1951representation}, we will be able
to interpret trees over an arbitrary semiring and satisfy the sequential
composition requirements. See an implementation
in~\cite{alga_haskell}.

@@

\noindent
It is useful to combine edge-labelled graphs with the sequential composition
law described in the previous section~(\S\ref{sec-preorder}). By computing the
reflexive and transitive closure of an edge-labelled graph, it is possible to
solve a variety of semiring optimisation problems, e.g.,
see~\cite{2013_semirings_dolan}\cite{mohri2002semiring}.
An implementation is available in~\cite{alga_haskell}.
